### 2023-04-07 chapter1/chapter1_supporting.tex
Moved supplementary information to end as appendices
Fixed some extra spaces in chapter1_supporting.tex tables
Moved chapter1_supporting.tex table labels after caption
Changed created to fit in phylogenetic tree sampling figure

\section*{Supporting information}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{trees/out/trees2_LG.png}
\centering
\caption{\textbf{Phylogenetic trees created by different sampling strategies under LG model.}}
\label{sfig:trees_LG}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{trees/out/trees2_GTR.png}
\centering
\caption{\textbf{Phylogenetic trees created by different sampling strategies under GTR model.}}
\label{sfig:trees_GTR}
\end{figure}

\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}

@@

\begin{table}[h!]
\centering
\caption{\textbf{Phylogenetic diversity criteria.}}
\begin{tabular}{|l|l|}
\hline
\textbf{Species   IDs} & \textbf{Minimum   number} \\ \hline
dinn,   dgri, dhyd     & 2                         \\ \hline
dnov,   dvir           & 1                         \\ \hline
dmoj,   dnav           & 1                         \\ \hline
dper,   dpse           & 1                         \\ \hline
dgua,   dsob           & 1                         \\ \hline
dana,   dbip           & 1                         \\ \hline
dkik,   dser           & 1                         \\ \hline
dele,   drho           & 1                         \\ \hline
dtak,   dbia           & 1                         \\ \hline
dspu,   dsuz           & 1                         \\ \hline
dere,   dtei           & 1                         \\ \hline
dsan,   dyak           & 1                         \\ \hline
dmel                   & 1                         \\ \hline
dmau,   dsec, dsim     & 1                         \\ \hline
\end{tabular}
\label{stable:diversity_criteria}
\end{table}

>>>>

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{trees/out/trees2_LG.png}
\centering
\caption{\textbf{Phylogenetic trees fit by different sampling strategies under LG model.}}
\label{sfig:trees_LG}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{trees/out/trees2_GTR.png}
\centering
\caption{\textbf{Phylogenetic trees fit by different sampling strategies under GTR model.}}
\label{sfig:trees_GTR}
\end{figure}

@@

\begin{table}[h!]
\centering
\caption{\textbf{Phylogenetic diversity criteria.}}
\label{stable:diversity_criteria}
\begin{tabular}{|l|l|}
\hline
\textbf{Species IDs}   & \textbf{Minimum number}   \\ \hline
dinn,   dgri, dhyd     & 2                         \\ \hline
dnov,   dvir           & 1                         \\ \hline
dmoj,   dnav           & 1                         \\ \hline
dper,   dpse           & 1                         \\ \hline
dgua,   dsob           & 1                         \\ \hline
dana,   dbip           & 1                         \\ \hline
dkik,   dser           & 1                         \\ \hline
dele,   drho           & 1                         \\ \hline
dtak,   dbia           & 1                         \\ \hline
dspu,   dsuz           & 1                         \\ \hline
dere,   dtei           & 1                         \\ \hline
dsan,   dyak           & 1                         \\ \hline
dmel                   & 1                         \\ \hline
dmau,   dsec, dsim     & 1                         \\ \hline
\end{tabular}
\end{table}
